Analysing the three-dimensional structure of {\em P. falciparum}

### 2017-07-09 doc/manuscript/paper.tex
Adding table

@@

@@

To assess whether groups of genes are colocolized in a 3D model,
\citet{ay:three-dimensional} leveraged a statistical method developped by
\citet{witten:XXX}, which requires labeling each pair of loci in two groups:
"close" or "far".

>>>>

In the past year, two groups have published novel dataset studying {\em P.
falciparum}'s 3D genome architecture using Hi-C. \citet{lemieux:genome-wide}
studied several strains associated with populations expression unique
\textit{var} genes, in order to study key folding properties of the 3D
structure relating to \textit{var} gene expression.
\citet{ay:three-dimensional} f three key-point of the development
cycle.

@@

\begin{table}
\footnotesize
\begin{tabular}{cccccc}
\hline
\textbf{Name} & \textbf{Strain} & \textbf{Stage} & \textbf{Resolution} &
\textbf{Number of contacts} & \textbf{Reference} \\
\hline
\hline
Ay-\textit{rings} & 3D7 & Late Rings & 10~kb & & \cite{ay:three-dimensional} \\
Ay-\textit{trophozoites} & 3D7 & Trophozoites &10~kb &  & \cite{ay:three-dimensional} \\
Ay-\textit{schizonts} & 3D7 & Schizonts & 10~kb & & \cite{ay:three-dimensional} \\
Lemieux-\textit{A4+} & IT/BC6+ & Rings & 25~kb & & \cite{lemieux:genome-wide} \\
Lemieux-\textit{A4} & IT/BC6- & Rings & 25~kb & & \cite{lemieux:genome-wide}\\
Lemieux-\textit{A4} & IT/3G8 & Rings &  25~kb & & \cite{lemieux:genome-wide}\\
Lemieux-\textit{DCJ\_On} & NF54/DCJ on & Rings & 25~kb &  &\cite{lemieux:genome-wide} \\
Lemieux-\textit{DCJ\_Off} & NF54/DCF Off & Rings & 25~kb &  &\cite{lemieux:genome-wide} \\
Lemieux-\textit{B15C2} & NF54/B15C2 & Rings & 25~kb &  & \cite{lemieux:genome-wide}\\
\hline
\end{tabular}
\caption{Summary of the available {\em P. falciparum} Hi-C datasets}{ The
number}
\end{table}

@@

To assess whether groups of genes are colocolized in a 3D model,
\citet{ay:three-dimensional} leveraged a statistical method developped by
\citet{witten:assessment}, which requires labeling each pair of loci in two groups:
"close" or "far".
